{\bf {\Large Evaluation and correction of noise related to physical processes in estimates of estuary metabolism}}

### 2014-08-22 swmp_noise.Rnw
finished tweaks to methods (removal of tidal categories, smaller hour windows), some proofing, added multimedia

@@

% dependent data
<<dep_dat, eval = T, echo = F, results = 'hide', child = 'dep_dat.Rnw'>>=
@

@@

% plot of representative time series for simulation
\centering\vspace*{\fill}
<<sim_ex, fig.height = 6.5, fig.width = 7, cache = T, echo = F, eval = T, fig.cap = 'Representative examples of simulated \\ac{DO} time series created by varying each of five parameters: tidal category (e.g., Mixed), strength of tidal association with \\ac{DO} signal using $DO_{adv}$, amount of process uncertainty $\\epsilon_{pro}$, amount of observation observation uncertainty $\\epsilon_{obs}$, and strength of diel \\ac{DO} component $DO_{die}$.  Parameter values represent the extremes used in the simulation (i.e., minimum, maximum).  Black lines are observed \\ac{DO} from \\cref{do_obs_all} and red lines are biological \\ac{DO} from \\cref{do_bio}.'>>=
load('eval_grd.RData')

@@

# setup facet labels
facet1_names <- list(
  'Diurnal' = expression(Diurnal), 
  'Semidiurnal' = expression(Semidi.), 
  'Mixed Semidiurnal' = expression(Mixed)
  )
facet2_names <- list(
  'Assoc 0' = expression(paste(italic(DO [adv]), ' 0')), 
  'Assoc 2' = expression(paste(italic(DO [adv]), ' 2'))
  )
facet3_names <- list(
  'Bio Amp 0' = expression(paste(italic(DO [die]), ' 0')), 
  'Bio Amp 2' = expression(paste(italic(DO [die]), ' 2'))
  )
facet4_names <- list(
  'Noise pro 0' = expression(paste(italic(epsilon [pro]), ' 0')), 
  'Noise pro 2' = expression(paste(italic(epsilon [pro]), ' 2'))
  )
facet5_names <- list(
  'Noise obs 0' = expression(paste(italic(epsilon [obs]), ' 0')), 
  'Noise obs 2' = expression(paste(italic(epsilon [obs]), ' 2'))
  )
plot_labeller <- function(variable,value){
  if (variable=='tide_cat')
    return(facet1_names[value])
  if (variable=='tide_assoc')
    return(facet2_names[value])
  if (variable=='bio_rng')
    return(facet3_names[value])
  if (variable=='err_rng_pro')
    return(facet4_names[value])
  if (variable=='err_rng_obs')
    return(facet5_names[value])
  }

ggplot(to_plo, aes(x = Day, y = DO_obs, group = L1)) + 
  geom_line() +
  geom_line(aes(y = DO_bio, colour = 'DO_bio'), alpha = 0.8) +
  theme_bw() + 
  theme(legend.position = 'none', axis.text.x = element_text(size = 8)) + 
  ylab(expression(paste('DO (mg ', L^-1, ')'))) +
  facet_grid(bio_rng + err_rng_obs + err_rng_pro ~ tide_cat + tide_assoc, 
    labeller = plot_labeller) 
@
\vfill
\clearpage

% example of error surfaces 
\centering\vspace*{\fill}
<<err_surf1, fig.height = 7, fig.width = 6, cache = T, echo = F, eval = T, fig.cap = "Correlations and errors (\\ac{RMSE}) for detided \\ac{DO} time series, $DO_{dtd}$, from weighted regression with `true' biological \\ac{DO}, $DO_{bio}$, for varying simulation parameters: tidal category (e.g., Mixed), strength of tidal association with \\ac{DO} signal $DO_{adv}$, amount of process uncertainty $\\epsilon_{pro}$, amount of observation observation uncertainty $\\epsilon_{obs}$, and strength of diel \\ac{DO} component $DO_{die}$.  Each tile represents the correlation or error between detided and biological \\ac{DO} time series from results for a given combination of simulation parameters.  Results are averaged for all window widths used to evaluate the regressions.">>=

@@

# aggregate for simpler plot
to_plo <- ddply(
  to_plo, 
  .variable = c('tide_cat','bio_rng', 'tide_assoc', 'err_rng_pro', 'err_rng_obs'),
  .fun = function(x) data.frame(cor = mean(x$cor), err = mean(x$err))
  )

# reassign factor labels for bio amp and tidal assoc
labs <- c('Diurnal', 'Semid.', 'Mixed')
to_plo$tide_cat <- factor(to_plo$tide_cat, levels = c('Diurnal', 
  'Semidiurnal', 'Mixed Semidiurnal'), labels = labs)
labs <- paste('Bio Amp', unique(to_plo$bio_rng))
to_plo$bio_rng <- factor(to_plo$bio_rng, labels = labs)
labs <- paste('Assoc',unique(to_plo$tide_assoc))
to_plo$tide_assoc <- factor(to_plo$tide_assoc, labels = labs)

# setup facet labels
facet1_names <- list(
  'Diurnal' = 'Diurnal',
  'Semid.' = 'Semid.',
  'Mixed' = 'Mixed'
  )
facet2_names <- list(
  'Bio Amp 0' = expression(paste(italic(DO [die]), ' 0')), 
  'Bio Amp 1' = expression(paste(italic(DO [die]), ' 1')),
  'Bio Amp 2' = expression(paste(italic(DO [die]), ' 2'))
  )
facet3_names <- list(
  'Assoc 0' = expression(paste(italic(DO [adv]), ' 0')), 
  'Assoc 1' = expression(paste(italic(DO [adv]), ' 1')),
  'Assoc 2' = expression(paste(italic(DO [adv]), ' 2'))
  )

plot_labeller <- function(variable,value){
  if (variable=='tide_cat')
    return(facet1_names[value])
  if (variable=='tide_assoc')
    return(facet2_names[value])
  if (variable=='bio_rng')
    return(facet3_names[value])
  }

@@

p1 <- ggplot(to_plo, aes(x = factor(err_rng_pro), y = factor(err_rng_obs), z = cor, fill = cor)) + 
  geom_tile() +
  facet_grid(tide_cat + bio_rng ~ tide_assoc,
    labeller = plot_labeller) +
  scale_fill_gradientn(name = 'Correlation', 
    colours = brewer.pal(11, 'Spectral'), limits = c(0, 1)
    ) +
  scale_x_discrete(expand = c(0,0)) + 
  scale_y_discrete(expand = c(0,0)) +
  xlab(expression(italic(epsilon [pro]))) +
  ylab(expression(italic(epsilon [obs]))) + 
  theme_bw() +
  mat_theme

p2 <- ggplot(to_plo, aes(x = factor(err_rng_pro), y = factor(err_rng_obs), z = err, fill = err)) + 
  geom_tile() +
  facet_grid(tide_cat + bio_rng ~ tide_assoc,
    labeller = plot_labeller) +
  scale_fill_gradientn(name = 'RMSE', 
    colours = rev(brewer.pal(11, 'Spectral')), limits = c(0, 2.5)
    ) +
  scale_x_discrete(expand = c(0,0)) + 
  scale_y_discrete(expand = c(0,0)) +
  xlab(expression(italic(epsilon [pro]))) +
  ylab(expression(italic(epsilon [obs]))) + 
  theme_bw() +
  mat_theme

@@

% example of error surfaces 
\centering\vspace*{\fill}
<<err_surf2, fig.height = 2.33, fig.width = 6, cache = T, echo = F, eval = T, fig.cap = "Correlations and errors (\\ac{RMSE}) for detided \\ac{DO} time series, $DO_{dtd}$, from weighted regression with `true' biological \\ac{DO}, $DO_{bio}$, for varying half window widths: days, hour of day, and proportion of tidal range.  Each tile represents the correlation or error between detided and biological \\ac{DO} time series from results for a given combination of window widths.  Results are averaged for all simulation parameters used to evaluate the regressions.">>=

@@

p1 <- ggplot(to_plo, aes(x = factor(dec_time), y = factor(hour), z = cor, fill = cor)) + 
  geom_tile() +
  facet_grid(~ Tide) +
  scale_fill_gradientn(name = 'Correlation', 
    colours = brewer.pal(11, 'Spectral'), limits = c(0.3, 0.7),
    breaks = seq(0.3, 0.7, by = 0.1)
    ) +
  scale_x_discrete(expand = c(0,0)) +
  scale_y_discrete(expand = c(0,0)) +
  xlab('Days') +
  ylab('Hours') + 
  theme_bw() +
  mat_theme

p2 <- ggplot(to_plo, aes(x = factor(dec_time), y = factor(hour), z = err, fill = err)) + 
  geom_tile() +
  facet_grid(~ Tide) +
  scale_fill_gradientn(name = 'RMSE', 
    colours = rev(brewer.pal(11, 'Spectral')), limits = c(1, 1.5), 
    labels = format(seq(1, 1.5, by = 0.1), nsmall = 1)
    ) +
  scale_x_discrete(expand = c(0,0)) + 
  scale_y_discrete(expand = c(0,0)) +
  xlab('Days') +
  ylab('Hours') + 
  theme_bw() +
  mat_theme

@@

% example from RKBMB
\centering\vspace*{\fill}
<<case_ex1, cache = T, fig.height = 6.5, fig.width = 5.5, out.width = '0.8\\textwidth', eval = T, echo = F, fig.cap = 'Example of daily mean metabolism (top) and continuous \\ac{DO} time series (middle) before (observed) and after (detided) detiding with weighted regression. Tidal height colored by total photosynthetically active radiation (mmol m$^{-2}$) is on the bottom plot. Results are for the Rookery Bay station for twenty days in August, 2012 using a weighted regression with window of eight days, six hours within each day, and tidal height proportion of one.'>>=
######
# RKBMB example

@@

# subsets by case. date range, window comb
case <- 'RKBMB'
dat.rng<-as.Date(c('2012-08-01','2012-08-20')) 
sel_vec <- with(case_grds, which(dec_time == 8 & hour == 6 & Tide == 1))
sel_vec <- paste0(case, '_wtreg_', sel_vec, '.RData')

# select case, window
met_subs <- met_ls[[grep(sel_vec, names(met_ls))]]
load(paste0('wtreg/', sel_vec))
inst_subs <- get(gsub('.RData', '', sel_vec))

# subset yby date
met.rng <- met_subs$Date<=dat.rng[2] & met_subs$Date>=dat.rng[1]
met_subs <- met_subs[met.rng,]

inst_subs$Date <- as.Date(inst_subs$DateTimeStamp)
inst.rng <- inst_subs$Date<=dat.rng[2] & inst_subs$Date>=dat.rng[1]
inst_subs <- inst_subs[inst.rng,]

@@

##
# DO plot
to_plo2 <- met.day.fun(inst_subs, case)
names(to_plo2)[names(to_plo2) %in% 'variable'] <- 'solar'
ggpoly <- poly.fun(to_plo2$solar, to_plo2)

ylab<-expression(paste('DO (mg ',L^-1,')'))
p2 <- ggplot(to_plo2, aes(x = DateTimeStamp)) + 
  ggpoly +
  geom_line(aes(y = DO_obs, colour = 'Observed')) +
  geom_line(aes(y = DO_nrm, colour = 'Detided')) +
  coord_cartesian(ylim = c(0,7)) +
  scale_fill_manual(values='orange',labels='Day') +
  theme_bw() +
  scale_y_continuous(ylab)  +
  my_theme

## 
# tide plot
to_plo3 <- met.day.fun(inst_subs, case)
names(to_plo2)[names(to_plo2) %in% 'variable'] <- 'solar'
ggpoly <- poly.fun(to_plo2$solar, to_plo2)

ylab<-expression(paste('Height (m)'))
p3 <- ggplot(to_plo3, aes(x = DateTimeStamp)) + 
  ggpoly +
  geom_line(aes(y = Tide, colour = TotPAR)) +
  coord_cartesian(ylim = rng.fun(to_plo3$Tide)) +
  scale_fill_manual(values='orange',labels='Day') +
  theme_bw() +  
  my_theme + 
  scale_y_continuous(ylab) +
  scale_colour_gradient("PAR", low='blue', high='yellow',
    guide = guide_colorbar(direction = "horizontal",barheight= 0.3))

# Get the widths
pA <- ggplot_gtable(ggplot_build(p1))
pB <- ggplot_gtable(ggplot_build(p2))
pC <- ggplot_gtable(ggplot_build(p3))
maxWidth = unit.pmax(pA$widths[2:3], pB$widths[2:3], 
                     pC$widths[2:3])

# Set the widths
pA$widths[2:3] <- maxWidth
pB$widths[2:3] <- maxWidth
pC$widths[2:3] <- maxWidth

grid.arrange(pA, pB, pC, ncol = 1, heights = c(1.7, 1, 1))

% example from SAPDC
\centering\vspace*{\fill}
<<case_ex2, cache = T, fig.height = 6.5, fig.width = 5.5, out.width = '0.8\\textwidth', eval = T, echo = F, fig.cap = 'Example of daily mean metabolism (top) and continuous \\ac{DO} time series (middle) before (observed) and after (detided) detiding with weighted regression. Tidal height colored by total photosynthetically active radiation (mmol m$^{-2}$) is on the bottom plot. Results are for the Sapelo Island station for a twenty day period in February, 2012 using weighted regression with a window of eight days, six hours within each day, and tidal height proportion of one.'>>=
######
# SAPDC example

# subsets by case. date range, window comb
case <- 'SAPDC'
dat.rng<-as.Date(c('2012-02-01','2012-02-20')) 
sel_vec <- with(case_grds, which(dec_time == 8 & hour == 6 & Tide == 1))
sel_vec <- paste0(case, '_wtreg_', sel_vec, '.RData')

# select case, window
met_subs <- met_ls[[grep(sel_vec, names(met_ls))]]
load(paste0('wtreg/', sel_vec))
inst_subs <- get(gsub('.RData', '', sel_vec))

# subset yby date
met.rng <- met_subs$Date<=dat.rng[2] & met_subs$Date>=dat.rng[1]
met_subs <- met_subs[met.rng,]

inst_subs$Date <- as.Date(inst_subs$DateTimeStamp)
inst.rng <- inst_subs$Date<=dat.rng[2] & inst_subs$Date>=dat.rng[1]
inst_subs <- inst_subs[inst.rng,]

##
# DO plot
to_plo2 <- met.day.fun(inst_subs, case)
names(to_plo2)[names(to_plo2) %in% 'variable'] <- 'solar'
ggpoly <- poly.fun(to_plo2$solar, to_plo2)

ylab<-expression(paste('DO (mg ',L^-1,')'))
p2 <- ggplot(to_plo2, aes(x = DateTimeStamp)) + 
  ggpoly +
  geom_line(aes(y = DO_obs, colour = 'Observed')) +
  geom_line(aes(y = DO_nrm, colour = 'Detided')) +
  coord_cartesian(ylim = c(1,10)) +
  scale_fill_manual(values='orange',labels='Day') +
  theme_bw() +
  scale_y_continuous(ylab)  +
  my_theme

## 
# tide plot
to_plo3 <- met.day.fun(inst_subs, case)
names(to_plo2)[names(to_plo2) %in% 'variable'] <- 'solar'
ggpoly <- poly.fun(to_plo2$solar, to_plo2)

ylab<-expression(paste('Height (m)'))
p3 <- ggplot(to_plo3, aes(x = DateTimeStamp)) + 
  ggpoly +
  geom_line(aes(y = Tide, colour = TotPAR)) +
  coord_cartesian(ylim = rng.fun(to_plo3$Tide)) +
  scale_fill_manual(values='orange',labels='Day') +
  theme_bw() +  
  my_theme + 
  scale_y_continuous(ylab) +
  scale_colour_gradient("PAR", low='blue', high='yellow',
    guide = guide_colorbar(direction = "horizontal",barheight= 0.3))

# Get the widths
pA <- ggplot_gtable(ggplot_build(p1))
pB <- ggplot_gtable(ggplot_build(p2))
pC <- ggplot_gtable(ggplot_build(p3))
maxWidth = unit.pmax(pA$widths[2:3], pB$widths[2:3], 
                     pC$widths[2:3])

# Set the widths
pA$widths[2:3] <- maxWidth
pB$widths[2:3] <- maxWidth
pC$widths[2:3] <- maxWidth

grid.arrange(pA, pB, pC, ncol = 1, heights = c(1.7, 1, 1))

@@

# subset metab estimates by 30 day window and tide prop 1
load('case_grds.RData')
sel_vec <- with(case_grds, which(dec_time == 8 & hour == 6 & Tide == 1))

@@

    # metabolism column names
    met_cols <- c('Pg', 'Rt', 'NEM', 'Pg_dtd', 'Rt_dtd', 'NEM_dtd')

@@

@@

latex( 
  tab,
  file = '',
  where = 'h',
  rowlabel = 'Parameter',
#   insert.bottom = foot.val,
  caption = cap.val,
  caption.loc = 'top',
  rgroup = Parms,
  n.rgroup = rep(3, 5),
  cgroup = c('Correlation', 'RMSE'),
  n.cgroup = c(5, 5),
  rowname = rows,
  colheads=rep(c('Min', '25\\textsuperscript{th}', 'Mean', '75\\textsuperscript{th}', 'Max'),2),
  label = 'tab:dtd_perf1'
  )
@

>>>>

% dependent data
<<dep_dat, eval = T, echo = F, cache = F, results = 'hide', child = 'dep_dat.Rnw'>>=
@

@@

@@

% plot of representative time series for simulation
\centering\vspace*{\fill}
<<sim_ex, fig.height = 4, fig.width = 7.5, out.width = '\\textwidth', cache = T, echo = F, eval = T, fig.cap = 'Representative examples of simulated observed \\ac{DO} ($DO_{obs}$) and biological \\ac{DO} ($DO_{bio})$ as a component of observed) time series created by varying each of four parameters: tidal strength of tidal association with \\ac{DO} signal using $DO_{adv}$, amount of process uncertainty $\\epsilon_{pro}$, amount of observation observation uncertainty $\\epsilon_{obs}$, and strength of diel \\ac{DO} component $DO_{die}$.  Parameter values represent the minimum and maximum used in the simulations.'>>=
load('eval_grd.RData')

@@

# setup facet labels
facet1_names <- list(
  'Assoc 0' = expression(paste(italic(DO [adv]), ' 0')), 
  'Assoc 2' = expression(paste(italic(DO [adv]), ' 2'))
  )
facet2_names <- list(
  'Bio Amp 0' = expression(paste(italic(DO [die]), ' 0')), 
  'Bio Amp 2' = expression(paste(italic(DO [die]), ' 2'))
  )
facet3_names <- list(
  'Noise pro 0' = expression(paste(italic(epsilon [pro]), ' 0')), 
  'Noise pro 2' = expression(paste(italic(epsilon [pro]), ' 2'))
  )
facet4_names <- list(
  'Noise obs 0' = expression(paste(italic(epsilon [obs]), ' 0')), 
  'Noise obs 2' = expression(paste(italic(epsilon [obs]), ' 2'))
  )
plot_labeller <- function(variable,value){
  if (variable=='tide_assoc')
    return(facet1_names[value])
  if (variable=='bio_rng')
    return(facet2_names[value])
  if (variable=='err_rng_pro')
    return(facet3_names[value])
  if (variable=='err_rng_obs')
    return(facet4_names[value])
  }

cols <- ggplotColours(2)
ggplot(to_plo, aes(x = Day, y = DO_obs, group = L1)) + 
  geom_line(aes(colour = 'Observed'), alpha = 0.7) +
  geom_line(aes(y = DO_bio, colour = 'Biological'), alpha = 0.7) +
  theme_bw() + 
  scale_colour_manual(
    labels = expression(italic(DO [bio]), italic(DO [obs])),
    values = cols
    ) +
  theme(legend.position = 'top', 
    legend.title = element_blank(), 
    axis.text = element_text(size = 8)
    ) + 
  ylab(expression(paste('DO (mg ', L^-1, ')'))) +
  facet_grid(err_rng_obs + err_rng_pro ~ bio_rng + tide_assoc, 
    labeller = plot_labeller) 
@
\vfill
\clearpage

% example of error surfaces 
\centering\vspace*{\fill}
<<err_surf1, fig.height = 3.5, fig.width = 5.5, cache = T, echo = F, eval = T, fig.cap = "Correlations and errors (\\ac{RMSE}) for detided \\ac{DO} time series, $DO_{dtd}$, from weighted regression with `true' biological \\ac{DO}, $DO_{bio}$, for varying simulation parameters: strength of tidal association with \\ac{DO} signal $DO_{adv}$, amount of process uncertainty $\\epsilon_{pro}$, amount of observation observation uncertainty $\\epsilon_{obs}$, and strength of diel \\ac{DO} component $DO_{die}$.  Each tile represents the correlation or error between detided and biological \\ac{DO} time series from results for a given combination of simulation parameters.  Results are averaged for all window widths used to evaluate the regressions (\\cref{fig:err_surf2}).">>=

@@

# aggregate for simpler plot
to_plo <- ddply(
  to_plo, 
  .variable = c('bio_rng', 'tide_assoc', 'err_rng_pro', 'err_rng_obs'),
  .fun = function(x) data.frame(cor = mean(x$cor), err = mean(x$err))
  )

# reassign factor labels for bio amp and tidal assoc
labs <- paste('Bio Amp', unique(to_plo$bio_rng))
to_plo$bio_rng <- factor(to_plo$bio_rng, labels = labs)
labs <- paste('Assoc',unique(to_plo$tide_assoc))
to_plo$tide_assoc <- factor(to_plo$tide_assoc, labels = labs)

# setup facet labels
facet1_names <- list(
  'Bio Amp 0' = expression(paste(italic(DO [die]), ' 0')), 
  'Bio Amp 1' = expression(paste(italic(DO [die]), ' 1')),
  'Bio Amp 2' = expression(paste(italic(DO [die]), ' 2'))
  )
facet2_names <- list(
  'Assoc 0' = expression(paste(italic(DO [adv]), ' 0')), 
  'Assoc 1' = expression(paste(italic(DO [adv]), ' 1')),
  'Assoc 2' = expression(paste(italic(DO [adv]), ' 2'))
  )

plot_labeller <- function(variable,value){
  if (variable=='tide_assoc')
    return(facet1_names[value])
  if (variable=='bio_rng')
    return(facet2_names[value])
  }

@@

p1 <- ggplot(to_plo, aes(x = factor(err_rng_pro), y = factor(err_rng_obs), z = cor, fill = cor)) + 
  geom_tile() +
  facet_grid(bio_rng ~ tide_assoc,
    labeller = plot_labeller) +
  scale_fill_gradientn(name = 'Correlation', 
    colours = brewer.pal(11, 'Spectral'), limits = c(0, 1)
    ) +
  scale_x_discrete(expand = c(0,0)) + 
  scale_y_discrete(expand = c(0,0)) +
  xlab(expression(italic(epsilon [pro]))) +
  ylab(expression(italic(epsilon [obs]))) + 
  theme_bw() +
  mat_theme

p2 <- ggplot(to_plo, aes(x = factor(err_rng_pro), y = factor(err_rng_obs), z = err, fill = err)) + 
  geom_tile() +
  facet_grid(bio_rng ~ tide_assoc,
    labeller = plot_labeller) +
  scale_fill_gradientn(name = 'RMSE', 
    colours = rev(brewer.pal(11, 'Spectral')), limits = c(0, 2.5)
    ) +
  scale_x_discrete(expand = c(0,0)) + 
  scale_y_discrete(expand = c(0,0)) +
  xlab(expression(italic(epsilon [pro]))) +
  ylab(expression(italic(epsilon [obs]))) + 
  theme_bw() +
  mat_theme

@@

% example of error surfaces 
\centering\vspace*{\fill}
<<err_surf2, fig.height = 2.33, fig.width = 6, cache = T, echo = F, eval = T, fig.cap = "Correlations and errors (\\ac{RMSE}) for detided \\ac{DO} time series, $DO_{dtd}$, from weighted regression with `true' biological \\ac{DO}, $DO_{bio}$, for varying half window widths: days, hour of day, and proportion of tidal range.  Each tile represents the correlation or error between detided and biological \\ac{DO} time series from results for a given combination of window widths.  Results are averaged for all simulation parameters used to evaluate the regressions (\\cref{fig:err_surf2}).">>=

@@

p1 <- ggplot(to_plo, aes(x = factor(dec_time), y = factor(hour), z = cor, fill = cor)) + 
  geom_tile() +
  facet_grid(~ Tide) +
  scale_fill_gradientn(name = 'Correlation', 
    colours = brewer.pal(11, 'Spectral')#, limits = c(0.3, 0.7),
#     breaks = seq(0.3, 0.7, by = 0.1)
    ) +
  scale_x_discrete(expand = c(0,0)) +
  scale_y_discrete(expand = c(0,0)) +
  xlab('Days') +
  ylab('Hours') + 
  theme_bw() +
  mat_theme

p2 <- ggplot(to_plo, aes(x = factor(dec_time), y = factor(hour), z = err, fill = err)) + 
  geom_tile() +
  facet_grid(~ Tide) +
  scale_fill_gradientn(name = 'RMSE', 
    colours = rev(brewer.pal(11, 'Spectral'))#, limits = c(1, 1.5), 
#     labels = format(seq(1, 1.5, by = 0.1), nsmall = 1)
    ) +
  scale_x_discrete(expand = c(0,0)) + 
  scale_y_discrete(expand = c(0,0)) +
  xlab('Days') +
  ylab('Hours') + 
  theme_bw() +
  mat_theme

@@

% example from SAPHD, phase out
\centering\vspace*{\fill}
<<phase_out, cache = T, fig.height = 3, fig.width = 5.5, out.width = '0.8\\textwidth', eval = T, echo = F, fig.cap = 'Continuous \\ac{DO} time series before (observed) and after (detided) detiding with weighted regression and tidal height colored by total photosynthetically active radiation (mmol m$^{-2}$). Results are for the Sapelo Island station for a seven day period when high tide events were out of phase with diel periods, creating lower than expected observed \\ac{DO} during night and day periods. Detided values are based on a weighted regression with half windows of six days, one hour within each day, and tidal height proportion of one half.'>>=
######
# SAPHD example

load('case_grds.RData')

# subsets by case. date range, window comb
case <- 'SAPDC'
dat.rng<-as.Date(c('2012-02-01','2012-02-14')) 
sel_vec <- with(case_grds, which(dec_time == casewins[[1]] & hour == casewins[[2]] & Tide == casewins[[3]]))
sel_vec <- paste0(case, '_wtreg_', sel_vec, '.RData')

load(paste0('wtreg/', sel_vec))
inst_subs <- get(gsub('.RData', '', sel_vec))

tzone <- attr(inst_subs$DateTimeStamp, 'tzone')

inst_subs$Date <- as.Date(inst_subs$DateTimeStamp, tz = tzone)
inst.rng <- inst_subs$Date<=dat.rng[2] & inst_subs$Date>=dat.rng[1]
inst_subs <- inst_subs[inst.rng,]

# category for plotting
inst_subs$cats <- 'out'
inst_subs$cats[inst_subs$Date > as.Date('2012-02-07')] <- 'in'

##
# custom theme, mod of theme_b
my_theme <- theme(
  legend.position = 'top',
  axis.title.x = element_blank(),legend.box= 'horizontal',
  plot.margin= unit(c(0, 1, 0, 1), "lines") # top right bottom left
  )

##
# out of phase plots

# DO plot
to_plo <- met.day.fun(inst_subs, case)
to_plo <- to_plo[to_plo$cats %in% 'out', ]
names(to_plo)[names(to_plo) %in% 'variable'] <- 'solar'
ggpoly1 <- poly.fun(to_plo$solar, to_plo, for_leg = T)
ggpoly2 <- poly.fun(to_plo$solar, to_plo)

ylab<-expression(paste('DO (mg ',L^-1,')'))
p1 <- ggplot(to_plo, aes(x = DateTimeStamp)) + 
  ggpoly1 +
  geom_line(aes(y = DO_obs, colour = 'Observed')) +
  geom_line(aes(y = DO_nrm, colour = 'Detided')) +
  coord_cartesian(ylim = rng.fun(to_plo$DO_obs)) +
  scale_fill_manual(values='orange',labels='Day') +
  theme_bw() +
  scale_y_continuous(ylab) +
  my_theme +
  theme(legend.title = element_blank())

#
# tide plot
ylab<-expression(paste('Height (m)'))
p2 <- ggplot(to_plo, aes(x = DateTimeStamp)) + 
  ggpoly2 +
  geom_line(aes(y = Tide, colour = TotPAR)) +
  coord_cartesian(ylim = rng.fun(to_plo$Tide)) +
  theme_bw() +  
  my_theme + 
  scale_y_continuous(ylab) +
  scale_colour_gradient("PAR", low='blue', high='yellow',
    guide = guide_colorbar(direction = "horizontal",barheight= 0.4)) +
  theme(legend.title.align = 1)

# get common legend, remove from p1
mylegend1 <- g_legend(p1)
mylegend2 <- g_legend(p2)
p1 <- p1 + theme(legend.position = 'none')
p2 <- p2 + theme(legend.position = 'none')

# Get the widths
pA <- ggplot_gtable(ggplot_build(p1))
pB <- ggplot_gtable(ggplot_build(p2))
maxWidth = unit.pmax(pA$widths[2:3], pB$widths[2:3])

# Set the widths
pA$widths[2:3] <- maxWidth
pB$widths[2:3] <- maxWidth

# first plot
grid.arrange(
  arrangeGrob(mylegend1, mylegend2, ncol = 1),    
  arrangeGrob(pA, pB, ncol = 1),
  ncol = 1, heights = c(2,5)
)

% example from SAPHD, phase in
\centering\vspace*{\fill}
<<phase_in, cache = T, fig.height = 3, fig.width = 5.5, out.width = '0.8\\textwidth', eval = T, echo = F, fig.cap = 'Continuous \\ac{DO} time series before (observed) and after (detided) detiding with weighted regression and tidal height colored by total photosynthetically active radiation (mmol m$^{-2}$). Results are for the Sapelo Island station for a seven day period when high tide events were in phase with diel periods, creating higher than expected observed \\ac{DO} during night and day periods. Detided values are based on a weighted regression with half windows of six days, one hour within each day, and tidal height proportion of one half.'>>=
######
# SAPHD example

load('case_grds.RData')

# subsets by case. date range, window comb
case <- 'SAPDC'
dat.rng<-as.Date(c('2012-02-01','2012-02-14')) 
sel_vec <- with(case_grds, which(dec_time == casewins[[1]] & hour == casewins[[2]] & Tide == casewins[[3]]))
sel_vec <- paste0(case, '_wtreg_', sel_vec, '.RData')

load(paste0('wtreg/', sel_vec))
inst_subs <- get(gsub('.RData', '', sel_vec))

tzone <- attr(inst_subs$DateTimeStamp, 'tzone')

inst_subs$Date <- as.Date(inst_subs$DateTimeStamp, tz = tzone)
inst.rng <- inst_subs$Date<=dat.rng[2] & inst_subs$Date>=dat.rng[1]
inst_subs <- inst_subs[inst.rng,]

# category for plotting
inst_subs$cats <- 'out'
inst_subs$cats[inst_subs$Date > as.Date('2012-02-07')] <- 'in'

##
# custom theme, mod of theme_b
my_theme <- theme(
  legend.position = 'top',
  axis.title.x = element_blank(),legend.box= 'horizontal',
  plot.margin= unit(c(0, 1, 0, 1), "lines") # top right bottom left
  )

##
# out of phase plots

# DO plot
to_plo <- met.day.fun(inst_subs, case)
to_plo <- to_plo[!to_plo$cats %in% 'out', ]
names(to_plo)[names(to_plo) %in% 'variable'] <- 'solar'
ggpoly1 <- poly.fun(to_plo$solar, to_plo, for_leg = T)
ggpoly2 <- poly.fun(to_plo$solar, to_plo)

ylab<-expression(paste('DO (mg ',L^-1,')'))
p1 <- ggplot(to_plo, aes(x = DateTimeStamp)) + 
  ggpoly1 +
  geom_line(aes(y = DO_obs, colour = 'Observed')) +
  geom_line(aes(y = DO_nrm, colour = 'Detided')) +
  coord_cartesian(ylim = rng.fun(to_plo$DO_obs)) +
  scale_fill_manual(values='orange',labels='Day') +
  theme_bw() +
  scale_y_continuous(ylab) +
  my_theme +
  theme(legend.title = element_blank())

#
# tide plot
ylab<-expression(paste('Height (m)'))
p2 <- ggplot(to_plo, aes(x = DateTimeStamp)) + 
  ggpoly2 +
  geom_line(aes(y = Tide, colour = TotPAR)) +
  coord_cartesian(ylim = rng.fun(to_plo$Tide)) +
  theme_bw() +  
  my_theme + 
  scale_y_continuous(ylab) +
  scale_colour_gradient("PAR", low='blue', high='yellow',
    guide = guide_colorbar(direction = "horizontal",barheight= 0.4)) +
  theme(legend.title.align = 1)

# get common legend, remove from p1
mylegend1 <- g_legend(p1)
mylegend2 <- g_legend(p2)
p1 <- p1 + theme(legend.position = 'none')
p2 <- p2 + theme(legend.position = 'none')

##
# in phase plots

# Get the widths
pA <- ggplot_gtable(ggplot_build(p1))
pB <- ggplot_gtable(ggplot_build(p2))
maxWidth = unit.pmax(pA$widths[2:3], pB$widths[2:3])

# Set the widths
pA$widths[2:3] <- maxWidth
pB$widths[2:3] <- maxWidth

# plot
grid.arrange(
  arrangeGrob(mylegend1, mylegend2, ncol = 1),    
  arrangeGrob(pA, pB, ncol = 1),
  ncol = 1, heights = c(2,5)
  )

% example from SAPDC
\centering\vspace*{\fill}
<<case_ex, cache = T, fig.height = 2.5, fig.width = 5.5, out.width = '0.8\\textwidth', eval = T, echo = F, fig.cap = 'Example of daily mean metabolism (net ecosystem metabolism, gross production, and total respiration) before (observed) and after (detided) detiding with weighted regression. Results are for the Sapelo Island station for a two week period in February, 2012 when high tide was out of phase with the diel cycle during the first week (\\cref{fig:phase_out}) and in phase during the second week (\\cref{fig:phase_in}).'>>=
######
# SAPDC example

@@

# subsets by case. date range, window comb
case <- 'SAPDC'
dat.rng<-as.Date(c('2012-02-01','2012-02-14')) 
sel_vec <- with(case_grds, which(dec_time == casewins[[1]] & hour == casewins[[2]] & Tide == casewins[[3]]))
sel_vec <- paste0(case, '_wtreg_', sel_vec, '.RData')

# select case, window
met_subs <- met_ls[[grep(sel_vec, names(met_ls))]]

# subset by date
met.rng <- met_subs$Date<=dat.rng[2] & met_subs$Date>=dat.rng[1]
met_subs <- met_subs[met.rng,]

@@

print(p1)

@@

# subset metab estimates by 30 day window and tide prop 1
load('case_grds.RData')
sel_vec <- with(case_grds, which(dec_time == casewins[[1]] & hour == casewins[[2]] & Tide == casewins[[3]]))

@@

    # metabolism column names
    met_cols <- c('Pg', 'Rt', 'Pg_dtd', 'Rt_dtd')

@@

# uses 'mod_perf' from, see readme
load('mod_perf.RData')

# calculate mean, se for dtd_cor and dtd_err
dtd_perf <- llply(names(mod_perf)[2:8], # note indexing
  .fun = function(x) {
    ddply(
      mod_perf,
      .variables = x,
      .fun = function(y) {
        c(
          min(y$cor),
          quantile(y$cor, 0.25),
          mean(y$cor),
          quantile(y$cor, 0.75),
          max(y$cor),
          min(y$err),
          quantile(y$err, 0.25),
          mean(y$err),
          quantile(y$err, 0.75),
          max(y$err)
        )
    })}
  )

@@

latex( 
  tab,
  file = '',
  where = 'h',
  rowlabel = 'Parameter',
#   insert.bottom = foot.val,
  caption = cap.val,
  caption.loc = 'top',
  rgroup = Parms,
  n.rgroup = rep(3, 4),
  cgroup = c('Correlation', 'RMSE'),
  n.cgroup = c(5, 5),
  rowname = rows,
  colheads=rep(c('Min', '25\\textsuperscript{th}', 'Mean', '75\\textsuperscript{th}', 'Max'),2),
  label = 'tab:dtd_perf1'
  )
@
